R Notebook

### 2017-04-13 doc/RMD/data-comparison.Rmd
update name of data
rerun with correct locus configuration
This ensures the MLGs are the same as the paper.

```{r merging_data}
corrected_loci <- ex %>% gather(locus, allele, -1) %>%
  left_join(exsummary, by = c("locus", "allele")) %>%
  mutate(allele = new_allele) %>%
  select(-new_allele) %>%
  spread(locus, allele) %>%
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  arrange(Isolate) %>%
  select(-(Severity:Host))
datdf <- genind2df(dat, usepop = FALSE) %>% 
  rownames_to_column(var = "Isolate") %>% 
  left_join(corrected_loci, by = "Isolate")
stopifnot(identical(datdf$Isolate, indNames(dat)))
dat   <- datdf %>% 
  select(-Isolate) %>% 
  df2genind(, ind.names = indNames(dat), strata = strata(dat), ploidy = 1) %>% 
  as.genclone()
```

@@

```{r, save_data}
save(dat, datdf, corrected_loci, file = "data/sclerotinia_16_loci.dat")
```

>>>>

```{r merging_data}
corrected_loci <- ex %>% gather(locus, allele, -1) %>%
  left_join(exsummary, by = c("locus", "allele")) %>%
  mutate(allele = new_allele) %>%
  select(-new_allele) %>%
  spread(locus, allele) %>%
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  arrange(Isolate) %>%
  select(-(Severity:Host))
datdf <- genind2df(dat, usepop = FALSE) %>% 
  rownames_to_column(var = "Isolate") %>% 
  left_join(corrected_loci, by = "Isolate")
stopifnot(identical(datdf$Isolate, indNames(dat)))
datdf <- datdf[c("Isolate", names(repeat_lengths))]
dat   <- datdf %>% 
  select(-Isolate) %>% 
  df2genind(ind.names = indNames(dat), strata = strata(dat), ploidy = 1) %>% 
  as.genclone()
```

@@

```{r}
setPop(dat) <- ~Region
dat
locNames(dat)
other(dat)$REPLEN
head(other(dat)$meta)
keeploci <- !locNames(dat) %in% colnames(corrected_loci)
dat11 <- dat[loc = keeploci, mlg.reset = TRUE] # reducing to 11 loci and recalculating mlgs
dat11
```

```{r, save_data}
save(dat, dat11, datdf, keeploci, corrected_loci, file = "data/sclerotinia_16_loci.rda")
```
